Analytics Without Tuning Considered Harmful?

### 2015-04-09 tuningpredictor.tex
Updates from ShareLaTeX

\begin{document}
% \conferenceinfo{FSE}{'15 Bergamo, Italy}
\title{ Analytics Without  Tuning Considered Harmful?}
% \numberofauthors{1}
\author{\alignauthor Wei Fu, Tim Menzies, Xipeng Shen \\
       \affaddr{Computer Science, North Carolina State University, Raleigh, USA}\\
       fuwei.ee, tim.menzies, xipengshen@gmail.com}
\maketitle
\pagestype{plain}
\begin{abstract}
One of the ``black arts'' of data mining is setting the tuning
parameters that control  the miner.  We offer a simple,
automatic, and very effective  method for finding those tunings.
For the purposes of learning
software defect predictors this  methid can quickly
find  good tunings that  dramatically change   the performance of a learner.
For example,
in this paper we show   tunings that  alter detection  precision  
 from 2\% to 98\%.

@@

Faced with this information overload,
researchers in empirical SE
use  data miners  to generate 
defect predictors from static code measures.
Such   measures can be
automatically extracted from the code base, with very little effort
even for very large software systems~\cite{nagappan05}.

One of the ``black arts'' of data mining is setting the tuning
parameters that control  the choices within that data miner.
Prior to this work, our intuition was that tuning would change the behavior or a data miner, to some degree. Nevertheless, we rarely tuned our  defect predictors 
since we reasoned
that a data miner's default tunings have been well-explored by the developers of those algorithms (in which case
tuning would not lead to large performance improvements).
Also, we suspected that
tuning would take so long and be so CPU intensive that the benefits gained   would not be worth effort.

The results of this paper show that neither of these points is supportable, at least when learning
defect detectors from static code attributes since:
\bi
\item
Tuning static code defect predictors is {\em remarkably simple} and can {\em dramatically improve the performance}. 
\ei
Prior to these experiments, our expectation was tuning
would be an  extensive and expensive evolutionary optimization procedure. 
A standard run of such evolutionary optimizers requires   thousands,
if not millions, of evaluations.
To
our surprise, we achieved dramatic improvements in the performance scores
of our data miners after  mere 50 to 80 evaluations (!!) of a very simple evolutionary 
optimizer  called differential evolution~\cite{storn1997differential}.
Better yet,  those  tunings (found so quickly)   
  have a dramatic change to the performance of a learner. For example,
in this paper we show that tuning can alter the precision of
a software defect predictor from 2\% to 98\%.

@@

Secondly, several  prominent IEEE TSE papers~\cite{lessmann2008benchmarking,hall11,me07b} have claimed 
that learnerX is better than learnerY for some software analytics task.
For example, a recent IEEE TSE article claimed that the 
CART decision tree learner was far worse than Random Forests for
software defect prediction~\cite{lessmann2008benchmarking}. 
Such conclusions do not survive tuning.
For example,
after tuning, the worst untuned learner (CART) can out-perform the supposedly
best learner (Random Forests). Hence, all those prior results that ranked learners for software
analytics now need to be revisited and perhaps revised.

@@

Linear  regression fits a  line to a set of points in order to minimize  predictive
error and maximizes the correlation\footnote{
{\em Correlation}
measures how closely two variables co-vary.  It ranges from   from -1
(perfect negative correlation) through 0 (no correlation) to +1
 (perfect positive correlation).
Let  $a_i$ and $p_i$ denote some actual and predicted values respectively; and  $n$ and $\overline{x}$ denote
 the number of observations and the mean of the $n$ observations, 
respectively. Then:
$S_{\mathit{PA}}=(\sum_i (p_i - \overline{p})(a_i -
  \overline{a}))/(n-1)$ and
$S_{p}=(\sum_i (p_i - \overline{p})^2)(n-1)$
and 
$S_{a}=(\sum_i (a_i - \overline{a})^2)/(n-1)$ and
correlation is  $c=S_{\mathit{PA}}/\sqrt{S_pS_a}$.}  denoted as $c$.
Suppose  a researcher wants to use linear regression
to test if Halstead's~\cite{halstead77} measures
of   function complexity
(number of symbols programmers has to understand) are   {\em better than}
mere lines of code for predicting
software defects.  That researcher might believe that Halstead's cognitive approach to
software bugs is better suited to code refactoring tools since it offers 
more ways to alter functions that just some coarse grain lines of code measure.

@@

The  point here is that   the true value of a detector
could not be assessed {\em without} conducting a  tuning study in the context of some business case (in this case, 
issuing a request to an inspection team to review some module).  
Hence, it is important to explore tuning
so the rest of this paper repeats the analysis of this section, but for 
more complex learners.

@@

This section is our standard introduction to defect prediction~\cite{me15:book1},
plus    new results from Rahman et al.~\cite{rahman14:icse}.

@@

\input{learners}

The psuedocode for differential evolution is shown in Algorithm~\ref{alg:DE}.
Note that, as we describe the algorithm,
  any superscript number denotes a line in that algorithm.

DE is an evolutionary algorithm where next {\em NewGeneration} is learnt from
a current {\em Population}.  If the new is no better than  current, then
we lose one life (terminating when lives is zero)$^5$.

Each candidate solution in the {\em Population}  
is a pair of {\em (Tunings, Scores)}.  {\em Tunings} are selected from
\fig{parameters} and {\em Scores} come from training a learner using those parameters
and applying it     test data$^{23-28}$.

The premise of DE  is that the best way to mutate existing tunings
is to {\em Extrapolate}$^{29}$
between current solutions.  Three solutions $a,b,c$ are selected at random.
For each tuning parameter $i$, at some probability {\em cr}, we replace
the old tuning $x_i$ with $y_i$:
\bi
\item (For numerics) $y_i = a_i+f \times (b_i - c_i)$   where $f$ is a parameter
controlling the cross-over amount.  The {\em trim} function$^{39}$ limits the new
value to the legal range min..max of that parameter.
\item (For booleans) $y_i= \neg x_i$ (see line 37).
\ei
The main loop of DE$^7$ runs over the {\em Population}, replacing old items
with new {\em Candidate}s (if the new candidate is better than the old item).
This means that, as the loop progresses, the {\em Population} is full of increasiningly
more valuable solutions. This, in turn, also improves  the candidates, which are generated
from the {\em Population}.

@@

Our defect data comes from the PROMISE repository\footnote{http://openscience.us/repo}.
It pertains to 
open source Java systems defined in terms of \fig{ck}:  {\it ant}, {\it camel}, {\it ivy}, {\it jedit}, {\it log4j}, {\it lucene},
{\it poi},{\it synapse}, {\it velocity} and {\it xerces}.

An important principle in data mining is not to test on the data used
in training.  There are many ways to design a experiment that satisfies this principle.
Some of those methods have  limitations:
\bi
\item  Leave-one-out is too slow for large data sets;
\item Cross-validation can mix up older and newer data sets so it may well be that
data from the {\em future} is used to test on {\em past data}.
\ei
To avoid these problems, we used an incremental learning approach. The following
experiment ensures that the training data was created at some time before the test
data.

For this experiment, we use data sets with at least three  
consecutive releases  (where release $i+1$ was built after release $i$).
\bi 
\item The {\em first} release was used for some  {\em training}, to collect a baseline
   using an untuned learner. This release is also used  on line 24 of Algorithm~\ref{alg:DE} to
   build some model using some the tunings found in some {\em Candidate}.
   \item The {\em second} release was used on 25 of Algorithm~\ref{alg:DE} to 
   test the model found on line 24.
   \item Finally the {\em third} release was used to gather the performance statistics
   reported below from (a)~the model generated by the untuned learner or (b)~the
   best model found by differential evolution.
   \ei
This approach ensures   all treatments 
are assessed on the same tests. Note that we did consider
one other experimental design but rejected it for reasons of
internal validity (see \tion{construct}).

@@

Recall from Algorithm~1 that we call differential evolution once for each
 optimization goal. This section lists those optimization goals.

Let $\{A,B,C,D\}$ denote the
true negatives, 
false negatives, 
false positives, and 
true positives
(respectively) found by a binary detector. 
Certain standard measures can be computed from
$A,B,C,D$:

@@

All the above vary from zero to one. For $pf$, the {\em better} scores are {\em smaller}.
For all other scores, the {\em better} scores are {\em larger}.
One technical detail:   {\em prec}
and {\em F} refer to {\em both} the defect and non-defective modules. This is different to {\em pf} and {\em recall} which only
refer to either non-defective or defective modules (repsectively).

\begin{figure}[!b]
\small
\begin{tabular}{|p{.95\linewidth}|}\hline
One style
of measure is to check the {\em variability} of that predictor.
For example,
in their study on reproducibility of SE results,
 Anda, Sjoberg and Mockus advocate using the coefficient of variation ($CV=\frac{stddev}{mean}$).
Using this measure, they defined {\em reproducibility} as $\frac{1}{CV}$~\cite{anda09}.

There exist other goals that combine defect prediction with other economic
factors.
Arisholm~\&~Briand~\cite{arisholm06},  Ostrand \& Weyeuker~\cite{ostrand04} and Rahman et al.~\cite{rahman12}
say that a defect predictor should maximizing {\em reward}; i.e. find the fewest lines of code
that contain the most bugs.

@@

In {\em Better-faster-cheaper},   managers want changes that lead
to fewer defects,  faster development,  using less resources~\cite{Green,elrawas08,elrawas10,me07f,me09a,me09f}.

Another  {\em  rush-to-market} approach is yet another economic-based optimization measure.
A learner that tries to maximize ``rush-to-market'' is trying to release the product as soon
as possible, without too many bugs. Note that ``rush-to-market'' is an appropriate strategy for a company competing
in a volatile and crowded market place where being first-to-market enables a revenue stream (that can be
used to subsequently fix any issues with version 1.0)~\cite{huang06}.\\\hline
\end{tabular}
\caption{Many ways to assess defect predictors.}\label{fig:criteria}
\end{figure}

Our analysis results make no assumption that (e.g.) minimizing false alarms is 
more important than maximizing   precision. That determination 
depends on current business conditions:
\be
\item
For safety critical applications, high false alarm rates may be acceptable if the cost
of overlooking any critical can outweigh the inconvenience of having to inspect a few more
modules. 
\item
On the other hand, when rushing a product to market before a competing product is released, there is a business case to 
avoid the extra rework associated with false alarms.  In that business context, 
managers might be willing to lower the recall somewhat in order to minimize the false alarms.
\ee
These two examples are just the tip of the iceberg (see other criteria in \fig{criteria})
and there is insufficient space in this paper to explore all the above optimization goals.
What we can do, however, is show examples of how  changing  optimization goals can also change 
the conclusions made from that learner on that data. Those examples only relate to precision, recall, and the F-measure
but the general principle (that the search bias changes the search conclusions) would hold for all the goals
listed in the previous paragraph.  Hence, we warn that it is important not to overstate  empirical results from software analytics.
Rather, those results need to be expressed {\em along with} the context within which they are
relevant (and by ``context'', we mean the optimization goal).

@@

The introduction of this article made several claims about tuning defect predictor
that use static code attributes. This section presents
support for those claims:
\be
\item  Tuning    improves the performance scores of a predictor;
e.g.  precision changes from 2\% to 98\%: see \tion{precision};
\item Tuning changes conclusions on what learners are better than others: see \tion{rank};
\item Tuning changes conclusions about what factors are most important: see \tion{import};
\item  Tuning is easy: see \tion{easy};
\item Tuning is fast: see \tion{fast};
\item Data miners should not be used ``off-the-shelf'' with their default tunings: see \tion{variance}.
\ee

One comment before continuing. The following text does not
show results for tuning on recall
or false alarms. The reason is that false alarm and recall focus on {\em only}
the non-defective and defective modules (respectively). Hence:
\bi
\item
When DE tunes for recall, we can achieve near
100\% recall-- but the cost of a near 100\% false alarms.
\item
Similarly, the tuner
could achieve near zero false alarm rates by effectively turning off
the detector (driving recall to zero).
\ei
Hence, in the
following, we explore performance measures that comment on all the possible
target classes (i.e. precision and ``F'').

@@

These results offer support for the prior conclusions of  
 Lessmann et al.~\cite{lessmann2008benchmarking} (that CART is worse than Random Forest):
\bi
\item
Untuned CART is indeed the worst learner (only one of its
untuned results is best and {\bf bold}). 
\item 
In $\frac{13}{17}$ cases, the performance of untuned Random Forest is better than or equal to untuned CART.  
\ei
% Some of the data sets in \fig{precisionbars} proved challenging for all learners;
% e.g. the precision results for {\em ivy} are less
% that impressive.
% To some extent, this is due to
% the properties of   the data set (as shown in \fig{data1}, defective classes in {\em ivy} are very rare in tuning data).

That said,  tuning can improve those poor performing detectors:
\bi
\item
For {\em jeditV2}, nearly all learners report precisions of under 20\%. But tuned  WHERE scores a 98\% precision.  
\item A similar pattern can be seen in results from {\em ivy},   and {\em xercesV0}.
In those two data sets, nearly all the precision values are   low {\em except} for
tuned WHERE that scored 89\% and 85\%.
\ei
Finally, note the  {\em jeditV2} result for the WHERE learner.
Here, tuning changes precision from 2\% to 98\%.

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=1.25in]{precision_W.eps}\includegraphics[width=1.25in]{F_W.eps}
 \end{center}
\caption{Deltas in performance  seen in \fig{precisionbars} (left)
and \fig{fbars} (right) between tuned and untuned learners. Tuning improves performance when the deltas are above zero.}\label{fig:deltas}
 \end{figure}

\subsection{Tuning Changes the Rankings of Learner  }\label{sect:rank}
Researchers often use performance criteria to assert that one learner is better than another~\cite{lessmann2008benchmarking,hall11,me07b}.
Such conclusions are   not reliable since they can change when we elect to tune for different goals.

For example, given the poor showing of untuned CART and the good performance of tuned WHERE
in   \fig{precisionbars}, we might recommend
{\em not} to use CART and {\em always} used tuned WHERE. In turns out that this
conclusion is not stable across the tuning process.

>>>>

\begin{document}
% \conferenceinfo{FSE}{'15 Bergamo, Italy}
\title{ Analytics Without  Tuning Considered Harmful?}
% \numberofauthors{1}
\author{\alignauthor Wei Fu, Tim Menzies, Xipeng Shen \\
       \affaddr{Computer Science, North Carolina State University, Raleigh, USA}\\
       fuwei.ee, tim.menzies, xipengshen@gmail.com}
\maketitle 
\thispagestyle{plain}
\pagestyle{plain}
\begin{abstract}
One of the ``black arts'' of data mining is setting the tuning
parameters that control  the miner.  We offer a simple,
automatic, and very effective  method for finding those tunings.
For the purposes of learning
software defect predictors this  methid can quickly
find  good tunings that  dramatically change   the performance of a learner.
For example,
in this paper we show   tunings that  alter detection  precision  
 from 2\% to 98\%.

@@

Faced with this information overload,
researchers in empirical SE
use  data miners  to generate 
{\em defect predictors from static code measures}.
Such   measures can be
automatically extracted from the code base, with very little effort
even for very large software systems~\cite{nagappan05}.

One of the ``black arts'' of data mining is setting the tuning
parameters that control  the choices within a data miner.
Prior to this work, our intuition was that tuning would change the behavior or a data miner, to some degree. Nevertheless, we rarely tuned our  defect predictors 
since we reasoned
that a data miner's default tunings have been well-explored by the developers of those algorithms (in which case
tuning would not lead to large performance improvements).
Also, we suspected that
tuning would take so long and be so CPU intensive that the benefits gained   would not be worth effort.

The results of this paper show that neither of these points is supportable, at least when learning
defect detectors from static code attributes since:
\be
\item
Tuning  defect predictors is {\em remarkably simple};
\item
And can {\em dramatically improve the performance}. 
\ee
Prior to these experiments, our expectation was tuning
would be an  extensive and expensive evolutionary optimization procedure. 
A standard run of such evolutionary optimizers requires   thousands,
if not millions, of evaluations.
To
our surprise, we achieved dramatic improvements in the performance scores
of our data miners after  mere 50 to 80 evaluations (!!) of a very simple evolutionary 
optimizer  called differential evolution~\cite{storn1997differential}.
Better yet,  those  tunings (found so quickly)   
  have a dramatic change to the performance of a learner. For example,
in this paper we show that tuning can alter the precision of
a software defect predictor from 2\% to 98\%.

@@

Secondly, several  prominent IEEE TSE papers~\cite{lessmann2008benchmarking,hall11,me07b} have claimed 
that learnerX is better than learnerY for some software analytics task.
For example, a recent IEEE TSE article claimed that the 
CART decision tree learner was far worse than Random Forests for
software defect prediction~\cite{lessmann2008benchmarking}. 
Such conclusions do not survive tuning.
For example,
after tuning, the worst untuned learner (CART) can perform just as well as the supposedly
best learner (Random Forest). Hence, all those prior results that ranked learners for software
analytics now need to be revisited (and perhaps revised).

@@

Suppose  a researcher wants to use linear regression
to test if Halstead's~\cite{halstead77} measures
of   function complexity
(number of symbols programmers has to understand) are   {\em better than}
mere lines of code for predicting
software defects.  That researcher might believe that Halstead's cognitive approach to
software bugs is better suited to code refactoring tools since it offers 
more ways to alter functions that just some coarse grain lines of code measure.

@@

The  point here is that   the true value of a detector
could not be assessed {\em without} conducting a  tuning study in the context of some business case (in this case, 
issuing a request to an inspection team to review some module).  
Hence, it is important to explore tuning.

The rest of this paper repeats the analysis of this section, but for 
more complex learners.

@@

This section is our standard introduction to defect prediction~\cite{me15:book1},
plus    some new results from Rahman et al.~\cite{rahman14:icse}.

@@

There are many ways to build defect predictors
such as  CART~\cite{brieman00}, Random Forest~\cite{breiman84}, 
and WHERE~\cite{menzies2013local}.
For this study, we use the CART and Random Forest  from 
SciKitLearn~\cite{scikit-learn} (and
WHERE is available from
github.com/ai-se/where).
 We use  these algorithms, for the following reasons.
CART and Random Forest were mentioned in
a recent IEEE TSE paper by Lessmann et al.~\cite{lessmann2008benchmarking} that compared 21  
learners for  defect prediction.
That study ranked  CART  worst  and Random Forest as best.
In a demonstration of the impact of tuning,
this paper shows  we can {\em reverse} the conclusions of  Lessmann et al. such that CART
performs just as well as
 Random Forest.
This
 paper also presents results with WHERE-based learner since, as shown below,
it offers an interesting case study on the benefits of tuning.

\subsection{Learners and Their Tunings}

Our learners use the tuning parameters of \fig{parameters}. This section describes those parameters.

CART, Random Forest, and WHERE-based learner are all  tree learners that divide a data set, then recurse
on each split.
All these learners
generate numeric predictions which are converted
into binary ``yes/no'' decisions via \eq{yesno}. Hence, they all use the {\em threshold} value $T$ discussed in \tion{eg}.

The splitting process is controlled by numerous tuning parameters.
If data contains more than {\em min\_sample\_split}, then a split is attempted.
On the other hand, if a split contains no more than {\em min\_samples\_leaf}, then recursion stops. For CART and Random Forest use a 
user-supplied constant for this parameter while
WHERE-based learner firstly computes this parameter $m$={\em min\_samples\_leaf} from the size of the data
sets via  $m=\mathit{size}^\mathit{min\_size}$ to build an initial  clustering tree.
Note that WHERE builds {\em two} trees: the initial clustering tree (to find similar sets of data)
then a final decision tree (to learn rules that predict for each similar cluster)\footnote{A
frequently asked question is why does WHERE build two trees--
would not   a single tree suffice? The answer is, as shown below,  tuned WHERE's twin-tree approach 
generates very precise predictors.}.
The tuning parameter  {\em min\_sample\_ split } controls the construction of the
final decision tree (so, for WHERE-based learner,
{\em min\_size} and {\em min\_sample\_split} are the parameters to be tuned).

These learners use different techniques to explore the splits:
\bi
\item
CART finds the attributes whose ranges contain rows with least variance in the number
of defects\footnote{If an attribute ranges $r_i$ is found in 
$n_i$ rows each with a  defect count variance of $v_i$, then CART seeks the attributes
whose ranges minimizes $\sum_i \left(\sqrt{v_i}\times n_i/(\sum_i n_i)\right)$.}.
\item
Random Forest    divides data like CART then  builds $F>1$  trees,
each time using some random subset of
the attributes. 
\item
When building the initial cluster tree, WHERE projects the data on to a dimension it synthesizes from the raw data using
a process analogous to principle component analysis\footnote{
PCA  synthesises  new
attributes $e_i, e_2,...$
that extends across the dimension of greatest  variance in the data  with attributes $d$.  
This process  combines
redundant  variables into a smaller set of variables  (so $e \ll d$) since those
redundancies become (approximately) parallel lines
in $e$ space. For all such redundancies \mbox{$i,j \in d$}, we 
can ignore $j$ 
since effects that change over $j$ also
change in the same way over $i$.
PCA is also useful for skipping over noisy variables from $d$-- these
variables are effectively ignored since    they  do not contribute to the variance in the data.}.
WHERE  divides  at the median point of that projection.
On recursion,
this generates the initial clustering tree, the leaves of which are clusters of  very similar examples. After that, when building 
the final decision tree, WHERE pretends its clusters are ``classes'', then 
asks the InfoGain of the
Fayyad-Irani discretizer~\cite{FayIra93Multi}, to rank the attriubutes, where {\em infoPrune} is used.
WHERE's final decision tree generator then ignores everything except the top   {\em infoPrune} percent of the sorted
attributes.
\ei
Some tuning parameters are learner specific:
\bi
\item
{\em Max\_feature} is used by
CART and Random Forest to select the number of attributes
used to build one tree.
CART's default is to use all the attributes while 
Random Forest usually selects the square root of the number
of attributes.
\item
  {\em Max\_leaf\_nodes} is the upper bound on leaf notes generated in a 
  Random Forest.
\item {\em Max\_depth} is the upper bound on the depth of the CART tree.  
 \item
WHERE's initial clustering
tree generation will always split up to {\em depthMin} number of branches.
After that, WHERE will only split data if the mean performance scores of the two halves
is ``trivially small'' (where ``trivially small'' is set by the   {\em wriggle} parameter). 
\item
WHERE's   {\em tree\_prune} setting controls how   
WHERE prunes back superflous parts of the final decision tree. 
If a decision sub-tree and its parent have the same 
majority cluster
(one that occurs most frequently), then if {\em tree\_prune} is enabled, we prune that decision sub-tree.
\ei

\subsection{Tuning Algorithms}

 \subsubsection{Parametric Tuning Algorithms}
The  goal of this paper is to adjust the tuning parameters of \fig{parameters}
in order to   optimize (improve) some particular performance scores
generated by a particular learner being applied to  a particular data set.
For this task, we do not use traditional parametric numeric optimizer  
such as  gradient descent optimizers~\cite{saltelli00} that require models comprised of
differential functions (i.e. functions of real-valued variables whose derivative exists at each point in its domain).
This is impractical  for  our learners since their internal states are   not a smoothly differential continuous function.
Rather, learners being tuned  contain many regions with many different properties (tuning options can
drive the learner into very different modes with very different performance properties).

 \subsubsection{Non-Parametric Tuning Algorithms}

Non-parametric  optimizers   make no assumption
about the internal structure of the model.
There are many such optimizers:
\bi
\item
Simulated annealing~\cite{fea02a,me07f};
\item
A wide range of genetic algorithms~\cite{goldberg79} augmented by
techniques such as differential evolution~\cite{storn1997differential}, tabu search and scatter search~\cite{Glover1986563,Beausoleil2006426,Molina05sspmo:a,4455350};
\item
Particle swarm optimization~\cite{pan08}; 
\item 
Numerous ``decomposition approaches'' that uses
    heuristics to decompose the total space into   small problems,   then applies a
    simpler optimizer to each region including \mbox{$\varepsilon$-domination}~\cite{deb05} and MOEA/D ~\cite{zhang07};
    \item 
    Response surface methods~\cite{krall15,Zuluaga:13};
    \item
    And many others as well.
    \ei
From all the above methods, how do we select which optimizers to apply to tuning data miners?
Cohen~\cite{cohen95} advises comparing new 
 methods against the simplest possible alternative. 
Holte~\cite{holte93} recommends using very simple  learners
 as a
kind of ``scout'' for a  preliminary analysis of a data
set (to check if that data really requires a more
complex analysis).

To find our ``scout'',  we used engineering judgement to sort  the above algorithms from simplest to most complex.
Of the optimizers listed above, the simplest are are SA  and 
differential evolution (each can be coded in less than a page of some high-level scripting language). Our reading of the current literature is that there are more  advocates for
differential evolution than
  SA:
  \bi
  \item
  When the MOEA/D community requires a secondary optimizer, they often use  differential evolution~\cite{zhang07,5583335}.
  \item
 Vesterstrom and Thomsen~\cite{Vesterstrom04} found DE to be competitive with 
   particle swarm optimization and other GAs.
   \ei
DEs have been applied before for   parameter tuning (e.g. see~\cite{omran2005differential, chiha2012tuning}) but this is the first time they have been applied to
optimize defect prediction from static code attributes.  
The psuedocode for differential evolution is shown in Algorithm~\ref{alg:DE}.
In the following description, 
    superscript numbers denotes a line in that figure.

DE is an evolutionary algorithm where the next {\em NewGeneration} is learnt from
a current {\em Population}.  Our DE's lose one ``life''
when e new is no better than  current (terminating when ``life'' is zero)$^5$.
Each candidate solution in the {\em Population}  
is a pair of {\em (Tunings, Scores)}.  {\em Tunings} are selected from
\fig{parameters} and {\em Scores} come from training a learner using those parameters
and applying it     test data$^{23-28}$.

The premise of DE  is that the best way to mutate existing tunings
is to {\em Extrapolate}$^{29}$
between current solutions.  Three solutions $a,b,c$ are selected at random.
For each tuning parameter $i$, at some probability {\em cr}, we replace
the old tuning $x_i$ with $y_i$:
\bi
\item (For numerics) $y_i = a_i+f \times (b_i - c_i)$   where $f$ is a parameter
controlling the cross-over amount.  The {\em trim} function$^{39}$ limits the new
value to the legal range min..max of that parameter.
\item (For booleans) $y_i= \neg x_i$ (see line 37).
\ei
The main loop of DE$^7$ runs over the {\em Population}, replacing old items
with new {\em Candidate}s (if the new candidate is better than the old item).
This means that, as the loop progresses, the {\em Population} is full of increasiningly
more valuable solutions. This, in turn, also improves  the candidates, which are {\em Extrapolate}d
from the {\em Population}.

@@

Our defect data comes from the PROMISE repository (http://openscience.us/repo)
and pertains to 
open source Java systems defined in terms of \fig{ck}:  {\it ant}, {\it camel}, {\it ivy}, {\it jedit}, {\it log4j}, {\it lucene},
{\it poi},{\it synapse}, {\it velocity} and {\it xerces}.

An important principle in data mining is not to test on the data used
in training.  There are many ways to design a experiment that satisfies this principle.
Some of those methods have  limitations; e.g.
{\em leave-one-out} is too slow for large data sets and
{\em cross-validation}   mixes up older and newer data  (such that
data from the {\em future} may be used to test on {\em past data}).

To avoid these problems, we used an incremental learning approach. The following
experiment ensures that the training data was created at some time before the test
data.
For this experiment, we use data sets with at least three  
consecutive releases  (where release $i+1$ was built after release $i$).
\bi 
\item The {\em first} release was used for some  {\em training}, to collect a baseline
   using an untuned learner. This release is also used  on line 24 of Algorithm~\ref{alg:DE} to
   build some model using some the tunings found in some {\em Candidate}.
   \item The {\em second} release was used on 25 of Algorithm~\ref{alg:DE} to 
   test the model found on line 24.
   \item Finally the {\em third} release was used to gather the performance statistics
   reported below from (a)~the model generated by the untuned learner or (b)~the
   best model found by differential evolution.
   \ei
This approach ensures   all treatments 
are assessed on the same tests. Note that we did consider
one other experimental design but rejected it for reasons of
internal validity (see \tion{construct}).

@@

Recall from Algorithm~1 that we call differential evolution once for each
 optimization goal. This section lists those optimization goals.
Let $\{A,B,C,D\}$ denote the
true negatives, 
false negatives, 
false positives, and 
true positives
(respectively) found by a binary detector. 
Certain standard measures can be computed from
$A,B,C,D$:

@@

For $pf$, the {\em better} scores are {\em smaller}.
For all other scores, the {\em better} scores are {\em larger}.
One technical detail:   {\em prec}
and {\em F} refer to {\em both} the defect and non-defective modules. This is different to {\em pf} and {\em recall} which only
refer to either non-defective or defective modules (repsectively).

\begin{figure}[!t]
\small
\begin{tabular}{|p{.95\linewidth}|}\hline

 Anda, Sjoberg and Mockus advocate using the coefficient of variation ($CV=\frac{stddev}{mean}$).
Using this measure, they defined {\em reproducibility} as $\frac{1}{CV}$~\cite{anda09}.

Arisholm~\&~Briand~\cite{arisholm06},  Ostrand \& Weyeuker~\cite{ostrand04} and Rahman et al.~\cite{rahman12}
say that a defect predictor should maximizing {\em reward}; i.e. find the fewest lines of code
that contain the most bugs.

@@

In {\em Better-faster-cheaper},   managers want
 fewer defects,  faster development,  using less resources~\cite{Green,elrawas10,me07f,me09f}.
\\\hline
\end{tabular}
\caption{Many ways to assess defect predictors.}\label{fig:criteria}
\end{figure}

This paper does not assume that (e.g.) minimizing false alarms is 
more important than maximizing   precision. Such a determination 
depends on   business conditions.
For example,
(1) for safety critical applications, high false alarm rates are  acceptable if the cost
of overlooking  critical issues outweighs the inconvenience of   inspecting a few more
modules. 
On the other hand, (2) when rushing a product to market,  there is a business case to 
avoid the extra rework associated with false alarms.  In that business context, 
managers might be willing to lower the recall somewhat in order to minimize the false alarms.
These two examples are just the tip of the iceberg (see other criteria in \fig{criteria})
and there is insufficient space in this paper to explore all the above optimization goals.

In this paper, what we can  show are examples of how  changing  optimization goals can also change 
the conclusions made from that learner on that data. Accordingly, we warn that it is important not to overstate  empirical results from software analytics.
Rather, those results need to be expressed {\em along with} the context within which they are
relevant (and by ``context'', we mean the optimization goal).

@@

This section offers empirical support for six claims:
\be
\item  Tuning    improves the performance scores of a predictor;
e.g.  precision changes from 2\% to 98\%: see \tion{precision};
\item Tuning changes conclusions on what learners are better than others: see \tion{rank};
\item Tuning changes conclusions about what factors are most important: see \tion{import};
\item  Tuning is easy: see \tion{easy};
\item Tuning is fast: see \tion{fast};
\item Data miners should not be used ``off-the-shelf'' with their default tunings: see \tion{variance}.
\ee

One comment before continuing. The following text does not
show results for tuning on recall
or false alarms. The reason is that false alarm and recall focus on {\em only}
the non-defective and defective modules (respectively). Hence:
\bi
\item
When DE tunes for recall, we can achieve near
100\% recall-- but the cost of a near 100\% false alarms.
\item
Similarly,  tuning
can achieve near zero false alarm rates by effectively turning off
the detector (when recall is zero).
\ei
Accordingly,  this paper  explores performance measures that comment on all 
target classes (i.e. precision and ``F'').

@@

These results offer support for  prior conclusions that CART is worse than Random Forest. As might have been
 predicted by Lessmann et al.~\cite{lessmann2008benchmarking}, 
untuned CART is indeed the worst learner (only one of its
untuned results is best and {\bf bold}). 
Also, 
in $\frac{13}{17}$ cases, the performance of untuned Random Forest is better than or equal to untuned CART.  
% Some of the data sets in \fig{precisionbars} proved challenging for all learners;
% e.g. the precision results for {\em ivy} are less
% that impressive.
% To some extent, this is due to
% the properties of   the data set (as shown in \fig{data1}, defective classes in {\em ivy} are very rare in tuning data).

That said,  tuning can improve those poor performing detectors.
For {\em jeditV2}, nearly all learners report precisions of under 20\%. But tuned  WHERE scores a 98\% precision.  
A similar pattern can be seen in results from {\em ivy},   and {\em xercesV0}.
In those two data sets, nearly all the precision values are   low {\em except} for
tuned WHERE that scored 89\% and 85\%.
Finally, note the  {\em jeditV2} result for the WHERE learner.
Here, tuning changes precision from 2\% to 98\%.

@@

\begin{figure}[!t]
\begin{center}
\includegraphics[width=1.5in]{precision_W.eps}\includegraphics[width=1.5in]{F_W.eps}
 \end{center}
\caption{Deltas in performance  seen in \fig{precisionbars} (left)
and \fig{fbars} (right) between tuned and untuned learners. Tuning improves performance when the deltas are above zero.}\label{fig:deltas}
 \end{figure}

\subsection{Tuning Changes the Rankings of Learner  }\label{sect:rank}
Researchers often use performance criteria to assert that one learner is better than another~\cite{lessmann2008benchmarking,hall11,me07b}.
Such conclusions are   not reliable since they can change when we elect to tune for different goals. 
For example, given the poor showing of untuned CART and the good performance of tuned WHERE
in   \fig{precisionbars}, we might recommend
{\em not} to use CART and {\em always} used tuned WHERE. In turns out that this
conclusion is not stable across the tuning process.
